abc

### 2024-10-06 randpython.qmd
trystackframe

```{pyodide-python}
import sympy, pandas, numpy, math
```

```{pyodide-python}
import sympy, pandas, numpy
from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
def rall(sel=[0, 0, 0]):
    n, m = symbols('n m')

@@

genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])[2]

@@

results = []
for nr in range(20):  # Example: looping from 0 to 19, you can change the range as needed
    lhs = test[2]['d'][nr]
    rhs = test[2]['expr'][nr]
    pareq_result = plsv.pareq(
        str(rhs),
        a1=a1, a2=a2, a3=a3,
        b1=b1, b2=b2, b3=b3,
        c1=c1, c2=c2, c3=c3,
        k0=k0, k1=k1, k2=k2, k3=k3, k4=k4, k5=k5, k6=k6, k7=k7, k8=k8, k9=k9
    )
    # Append the result dictionary directly to the list
    results.append({
        'lhs': lhs,
        'rhs': rhs,
        'pareq_result': pareq_result
    })

df_results = pd.DataFrame(results)
```

```{pyodide-python}
a1, a2, a3, b1, b2, b3, c1, c2, c3
```

```{pyodide-python}
# https://docs.google.com/spreadsheets/d/1Qf51QlYkCmd8h72R5JrFUt9VYCgpq8U_RyQTLzOoiFc/edit?gid=499474525#gid=499474525
df_results 
```

>>>>

```{pyodide-python}
import sympy, pandas, numpy, math
from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
def rall(sel=[0, 0, 0]):
    n, m = symbols('n m')

@@

# genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])[2]

@@

results = []
for nr in range(20):  # Example: looping from 0 to 19, you can change the range as needed
    lhs = test[2]['d'][nr]
    rhs = test[2]['expr'][nr]
    pareq_result = pareq(
        str(rhs),
        a1=a1, a2=a2, a3=a3,
        b1=b1, b2=b2, b3=b3,
        c1=c1, c2=c2, c3=c3,
        k0=k0, k1=k1, k2=k2, k3=k3, k4=k4, k5=k5, k6=k6, k7=k7, k8=k8, k9=k9
    )
    # Append the result dictionary directly to the list
    results.append({
        'lhs': lhs,
        'rhs': rhs,
        'pareq_result': pareq_result
    })

df_results = pandas.DataFrame(results)

```

# Output
```{pyodide-python}
a1, a2, a3, b1, b2, b3, c1, c2, c3
```

```{pyodide-python}
df_results
```
